Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-18 lqg-strings.tex
Sketched and added to main file further simplifications to the wave equation and modification to wave speed

>>>>

Rewriting eq(\ref{eqn:corrected-NG-wave-equation}) in terms of $\sigma$ derivatives and parameterizing $\sigma$ as (let $F = (1 - g \Delta / (2 (- h)))$)
\begin{equation} \label{eqn:sigma-parameterization}
	\sigma (q) = \frac{1}{T} \int _{0} ^{q} \diff E \frac{1}{F^2} ,
\end{equation}
we find the wave equation
\begin{equation} \label{eqn:simplified-modified-wave-eqn}
	F^2 \frac{\partial ^2 \Vec{X}}{\partial t^2} - \frac{\partial ^2 \Vec{X}}{\partial \sigma ^2} = 0 ,
\end{equation}
from which we can see that the correction factor modifies the speed of propagation of the wave in the string as
\begin{equation} \label{eqn:wave-speed-corrected}
	v = \frac{c}{|F|} .
\end{equation}
